Untitled

### 2021-02-01 ms/manuscript.Rmd
Use kableExtra for all tables

```{r glmm-table, results = "asis"}
glmm_summ_group_locs <-
glmm_summary %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    DIC = round_t(DIC, 2),
    delta_DIC = round_t(delta_DIC, 2)
  ) %>%
  select(fixed_effects, DIC, delta_DIC) %>%
  kbl(format = "latex", booktabs = TRUE, col.names = c("Fixed effects", "DIC", "delta DIC"), escape = TRUE) %>%
  row_spec(which(glmm_summary$delta_DIC == 0), bold = TRUE) %>%
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

glmm_params_cols <-
  c(
    "Fixed effects" = "fixed_effects", 
    "Predictor" = "predictor",
    "Mean effect" = "post.mean",
    "Lower 95\\% CI" = "l-95% CI",
    "Upper 95\\% CI" = "u-95% CI",
    "Ef. sample size" = "eff.samp",
    "\\textit{P} MCMC" = "pMCMC"
  )

glmm_params %>%
  mutate(
    fixed_effects = str_to_sentence(fixed_effects),
    predictor = str_replace_all(predictor, "generationsporophyte", "Sporophyte") %>%
      str_replace_all("habitLow_Epiphyte", "Low Epiphyte") %>%
      str_replace_all("habitSaxicolous", "Saxicolous") %>%
      str_replace_all("habitTerrestrial", "Terrestrial")
  ) %>%
  select(all_of(glmm_params_cols)) %>%
  kbl(format = "latex", booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "scale_down") %>%
  row_spec(which(glmm_params$pMCMC < 0.05), bold = TRUE) %>%
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_params_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

```{r pgls, results = "asis"}
env_range_dt_model_summary %>%
  mutate(generation = case_when(
    str_detect(model, "sporo") ~ "S",
    str_detect(model, "gameto") ~ "G"
  )) %>%
  assert(not_na, generation) %>%
  mutate(
    predictor = case_when(
      str_detect(model, "vpd") ~ "VPD",
      str_detect(model, "range") ~ "G beyond S"
    )
  ) %>%
  assert(not_na, predictor) %>%
  select(generation, predictor, df, f_value, adj_r_squared, p_value) %>%
  mutate(
    f_value = round_t(f_value, 3),
    p_value = round_t(p_value, 3),
    adj_r_squared = round_t(adj_r_squared, 3)
  ) %>%
  kbl(col.names = c("Generation", "Predictor", "df", "$F$", "adj. $R^2$", "$P$"), escape = FALSE, booktabs = TRUE)
```

>>>>

```{r glmm-table, results = "asis"}
# Make helper table for formatting by groups
glmm_summ_group_locs <-
glmm_summary %>% mutate(row_num = 1:nrow(.)) %>% group_by(response) %>%
  summarize(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

# Format column names.
# left side is new name (with latex formatting)
# right side is original name
glmm_summary_cols <-
  c(
    "Fixed effects" = "fixed_effects", 
    "DIC" = "DIC",
    "delta DIC" = "delta_DIC"
  )

glmm_summary %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    DIC = round_t(DIC, 2),
    delta_DIC = round_t(delta_DIC, 2)
  ) %>%
  select(all_of(glmm_summary_cols)) %>%
  kbl(format = "latex", booktabs = TRUE, escape = TRUE) %>%
  row_spec(which(glmm_summary$delta_DIC == 0), bold = TRUE) %>%
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_summ_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

# Format column names.
# left side is new name (with latex formatting)
# right side is original name
glmm_params_cols <-
  c(
    "Fixed effects" = "fixed_effects", 
    "Predictor" = "predictor",
    "Mean effect" = "post.mean",
    "Lower 95\\% CI" = "l-95% CI",
    "Upper 95\\% CI" = "u-95% CI",
    "Ef. sample size" = "eff.samp",
    "\\textit{P} MCMC" = "pMCMC"
  )

# Format cell values
glmm_params %>%
  mutate(
    fixed_effects = case_when(
      fixed_effects == "both" ~ "Generation + habit",
      fixed_effects == "intersect" ~ "Generation + habit + Generation:habit",
      TRUE ~ str_to_sentence(fixed_effects)
    ),
    predictor = str_replace_all(predictor, "generationsporophyte", "Sporophyte") %>%
      str_replace_all("habitLow_Epiphyte", "Low Epiphyte") %>%
      str_replace_all("habitSaxicolous", "Saxicolous") %>%
      str_replace_all("habitTerrestrial", "Terrestrial"),
    # Round off long numeric values
    across(c(post.mean, `l-95% CI`, `u-95% CI`, pMCMC), ~round_t(., 3)),
    eff.samp = as.integer(eff.samp)
  ) %>%
  # Format column names
  select(all_of(glmm_params_cols)) %>%
  kbl(format = "latex", booktabs = TRUE, escape = FALSE) %>%
  kable_styling(latex_options = "scale_down") %>%
  # Make significant rows bold
  row_spec(which(glmm_params$pMCMC < 0.05), bold = TRUE) %>%
  # Add group rows
  pack_rows(
    "ETR\\\\textsubscript{max}", 
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "etr") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "PPFD\\\\textsubscript{95\\\\%}", 
    glmm_params_group_locs %>% filter(response == "par") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "par") %>% pull(end),
    escape = FALSE) %>%
  pack_rows(
    "Recovery", 
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(start),
    glmm_params_group_locs %>% filter(response == "recovery") %>% pull(end),
    escape = FALSE)
```

@@

```{r pgls, results = "asis"}
# Format column names.
# left side is new name (with latex formatting)
# right side is original name
pgls_cols <-
  c(
    "Generation" = "generation", 
    "Predictor" = "predictor",
    "df" = "df",
    "\\textit{F}" = "f_value",
    "adj. \\textit{R}\\textsuperscript{2}" = "adj_r_squared",
    "\\textit{P}" = "p_value"
  )

# Format cell values
env_range_dt_model_summary %>%
  mutate(generation = case_when(
    str_detect(model, "sporo") ~ "S",
    str_detect(model, "gameto") ~ "G"
  )) %>%
  assert(not_na, generation) %>%
  mutate(
    predictor = case_when(
      str_detect(model, "vpd") ~ "VPD",
      str_detect(model, "range") ~ "G beyond S"
    )
  ) %>%
  assert(not_na, predictor) %>%
  mutate(
    f_value = round_t(f_value, 3),
    p_value = round_t(p_value, 3),
    adj_r_squared = round_t(adj_r_squared, 3)
  ) %>%
  # Format column names
  select(all_of(pgls_cols)) %>%
  kbl(format = "latex", escape = FALSE, booktabs = TRUE)
```
